---
title: "Google Analytics Customer: EDA"
author: "kotsubo takuto"
output: 
    html_document:
      md_extensions: -ascii_identifiers
      toc: true
      toc_depth: 3
      code_folding: hide
---

# Setting{.tabset .tabset-fade .tabset-pills}

## knitr option

```{r reset, include=FALSE}
# 初期化
rm(list = ls())
```

```{r set up, message=FALSE}
# set directory
setwd("~/Desktop/Google_Analytics_Kaggle/") 
# max.print 
options(max.print="200", digits=5)
# Global options
library(knitr)
opts_chunk$set(echo=TRUE,
               cache = FALSE,
	             prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Library package

```{r package, message=FALSE}
library(tidyverse)
library(readr) # for csv
library(summarytools) # summary easily for EDA
library(GGally) # ggpairs
library(skimr) 
library(janitor)
library(jsonlite)
```

## Load funciton

```{r}
source('~/Desktop/Google_Analytics_Kaggle/script/function.R') # for preprocessing
source('~/Desktop/Google_Analytics_Kaggle/script/makedummies.R') # for preprocessing
```

## Import csv

- Import raw data from `input/imp/{tarin|test}.csv`

```{r cache=TRUE}
# read impute data
train_imp <- read_csv("~/Desktop/Google_Analytics_Kaggle/input/imp/train_imp1.scv",
                      locale = readr::locale(date_format = "%Y%m%d"))
test_imp <- read_csv("~/Desktop/Google_Analytics_Kaggle/input/imp/test_imp1.csv",
                      locale = readr::locale(date_format = "%Y%m%d"))
```

# Explatory Data Analysis

- Apply glimpse and dfsummary to the all data
- Check three id values
- Confirm relationship with target variables -> 2_EDA.Rmd 

## Apply glimpse and dfsummary to the all data{.tabset .tabset-fade .tabset-pills}

### glimpse 

```{r cache=TRUE}
glimpse(train_imp1)
glimpse(test_imp1)
```

### dfsummary

```{r cache=TRUE}
dfSummary(train_imp1) %>% 
  view(method = "render")
dfSummary(test_imp1) %>% 
  view(method = "render")
```

## Check three id values

- `fullVisitorId`
- `sessionId`
- `visitId`

- uniqueな値を確認する. 

```{r}
# train
train_flat %>% distinct(fullVisitorId) %>% NROW
train_flat %>% distinct(sessionId) %>% NROW
train_flat %>% distinct(visitId) %>% NROW
# test
test_flat %>% distinct(fullVisitorId) %>% NROW
test_flat %>% distinct(sessionId) %>% NROW
test_flat %>% distinct(visitId) %>% NROW
```

- 2つのIDを組み合わせると, `sessionId` と同じ結果になる
- `visitId` 必要なのか?

```{r}
train_flat %>% distinct(fullVisitorId, visitId) %>% NROW
test_flat %>% distinct(fullVisitorId, visitId) %>% NROW
```

- train, testに同一のuserは出現していないか
- user id: 全1331409種 (unique value: 1323730)
- 同一のuserが存在する. 

```{r}
train_flat %>% 
  distinct(fullVisitorId) %>% 
  rbind(test_flat %>% distinct(fullVisitorId)) -> tmp
tmp %>% distinct(fullVisitorId) %>% NROW
```

- trainの購入履歴あり + test: 627,238 (unique: 626702)
- 536人は購入かつ再度訪問している.

```{r}
train_flat %>% 
  filter(!is.na(transactionRevenue)) %>% 
  distinct(fullVisitorId) %>% 
  rbind(test_flat %>% distinct(fullVisitorId)) -> tmp
tmp %>% distinct(fullVisitorId) %>% NROW
```
